Finite Property Convex Elicitation Paper

### 2019-01-25 cvx-fin.tex
Jessie starting prop 8 nd 9 proofs... brain pooped out on me.

\begin{definition}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if \raf{Shivani definition};
  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
  \end{itemize}
\end{definition}

@@

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  \raft{Jessie: I think this should be fine for the paper.  We may want strip and trim for the proof, in the appendix, in which case we can define them there...}
	Let $\Gamma:\simplex\toto\reals^d$ be a non-degenerate (convex) elicitable property.
    \raf{Do we really need $\Gamma$ to be convex elicitable?}

	The following are equivalent:
	\begin{enumerate}
		\item $\Gamma$ embeds a finite elicitable property.
		\item The set $\{\Gamma_r : r \in \R' \}$ is finite.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
	\end{enumerate}
\end{proposition}

@@

\begin{proposition}
  If $\Gamma$ embeds $\gamma$, then there is a link function $\psi$ between $\Gamma$ and $\gamma$.
  Moreover, if $L$ elicits $\Gamma$ and $L$ is polyhedral, $\psi$ can be taken to be separated.
\end{proposition}

@@

\begin{definition}
  Let $\Gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$.
  Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\R'$ we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r\in\R$.
  That is, the cells of $\Gamma'$ are all contained in cells of $\Gamma$.
\end{definition}

>>>>

\begin{definition}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$, 
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]
  \end{align*}
  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
  \end{itemize}
\end{definition}

@@

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  \raft{Jessie: I think this should be fine for the paper.  We may want strip and trim for the proof, in the appendix, in which case we can define them there...}
	Let $\Gamma:\simplex\toto\reals^d$ be a non-degenerate (convex) elicitable property.
    \raf{Do we really need $\Gamma$ to be convex elicitable?}
    \jessie{Not a requirement... I threw it in parentheses since we typically think of $\Gamma$ as elicited by a convex surrogate, but it isn't used in the proof.}

	The following are equivalent:
	\begin{enumerate}
		\item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
		\item The set $\{\Gamma_r : r \in \R \}$ is finite.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}
For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
Thus, the set generated by indexing a finite set is finite.
For $2 \implies 3$, assume each level set $\Gamma_r$ in the given set is full-dimensional without loss of generality...
\jessie{TODO}

For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
Let $\R$ be the collection of such reports $u$ corresponding to each level set.
The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
Since each level set is convex, we know $\gamma$ is elicitable.
\jessie{Cite?}
\end{proof}

@@

\begin{proposition}
  If $\Gamma$ embeds $\gamma$, then there is a link function $\psi$ between $\Gamma$ and $\gamma$.
  Moreover, if $L$ elicits $\Gamma$ and $L$ is polyhedral, $\psi$ can be taken to be separated.
\end{proposition}
\begin{proof}
Let $\varphi$ be the embedding function.
Then the function $\psi(u) := \varphi^{-1}(r)$ is a link between $\Gamma$ and $\gamma$.
Since, for all $p \in\simplex$, we know $\varphi(r) \in \Gamma(p) \implies \varphi^{-1}(\varphi(r)) = r \in \gamma(p)$, we can observe that $\psi$ is a calibrated link.

For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
Suppose $\Gamma$ is elicited by a polyhedral function and the link connecting $\gamma$ and $\Gamma$ was not separated.
Then either the embedded points are too close \jessie{...}.
If, for some $v \in B(\epsilon, u)$, we see $\psi(v) \neq \psi(u)$, then $\psi(v) \neq \psi(w)$ for some $w \neq u$.
\jessie{My brain is turning off and I didn't get to do nearly as much as I thought I was going to be able to tonight, but I'll iterate again in the morning.}
\end{proof}

@@

\begin{definition}
  Let $\Gamma:\simplex\toto\R$ and $\Gamma':\simplex\toto\R'$.
  Then $\Gamma'$ \emph{refines} $\Gamma$ if for all $r'\in\R'$ we have $\Gamma'_{r'} \subseteq \Gamma_r$ for some $r\in\R$.
  That is, the cells of $\Gamma'$ are all contained in cells of $\Gamma$.
\end{definition}
